---
title: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme : sandstone #readable #spacelab
    logo: www/logo.jpg
    css: www/styles.css
params:
  LIB: "JEFF"
  VER: "3.3"
  LIB2: "JEFF"
  VER2: "3.2"
  SDIR : "./"
---

<script> 
var $buoop = {notify:{e:-0.01,f:-0.01,o:-0.01,s:-0.01,c:-2},insecure:true,unsupported:true,style:"corner",api:5}; 
function $buo_f(){ 
 var e = document.createElement("script"); 
 e.src = "//browser-update.org/update.min.js"; 
 document.body.appendChild(e);
};
try {document.addEventListener("DOMContentLoaded", $buo_f,false)}
catch(e){window.attachEvent("onload", $buo_f)}
</script>

```{r setup, include=FALSE}
library(plotly)
library(shinythemes)
library(shinyjs)
library(DT)
library(data.table)
library(dplyr)
library(flexdashboard)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
# source(paste0(params$SDIR, '/global.R'))
load(paste0(params$SDIR, 'df.RData'))




#define parameters other than params 
mLIBVER <- paste(params$LIB, params$VER, sep = "-")
mLIBVER2 <- paste(params$LIB2, params$VER2, sep = "-")

# for flexdashboard : 
LIBLINK <-"https://www.oecd-nea.org/dbdata"
libcolor="#cce6ff"  #color of lib value box in headers
link_download="pathtosite"

# building columns in lib as html links : 
icon1 <- "<i class='fa fa-download'></i>"
icon2 <- "<i class='fa fa-sitemap'></i>"
icon3 <- "<i class='fa fa-file-alt'></i>"
icon4 <- "<i class='fa fa-file></i>"

# total number of files
totfiles <- df %>%
  subset(LIB==params$LIB & VER==params$VER, select=c("Z", "A", "M", "LIB", "VER")) %>%
  unique() %>%
  nrow()

#adding decay data: 
# lib<-merge(x=lib, y=decay, by=c('Z', 'A', 'M'), all.x=TRUE) # For the moment we do not do it

```


Maps
====

```{r child='barheader_libpage.Rmd'}
```



### **List of updated `r mLIBVER`  files with respect to previous release `r mLIBVER2` - Access individual Maps ** 


```{r table_diffs}
lib1 <- df %>% subset( LIB == params$LIB & VER == params$VER & MT != 451,
                       select=c(Z, A, M, SYMA, MF, MT, LIBVERORIG))
lib2 <- df %>% subset( LIB == params$LIB2 & VER == params$VER2 & MT != 451,
                       select=c(Z, A, M, SYMA, MF, MT, LIBVERORIG))
merge(lib1, lib2, by=c("Z","SYMA","M","MF","MT"), all.x=T) %>%
  dplyr::mutate(eq=LIBVERORIG.x==LIBVERORIG.y) %>%
  dplyr::mutate_at(vars("eq"), funs(if_else( is.na(.), F, .)) ) %>%
  dplyr::group_by(Z,SYMA,M) %>%
  dplyr::summarize(Updated=!(all(eq)==T)) %>%
  dplyr::mutate(
    # ENDF6 = paste(Z, SYMA, M, sep = "-") %>% paste0(".", tolower(LIB), gsub("[.]","",VER)), # Add ENDF-6 filename
    # ACE = paste(Z, SYMA, M, sep = "-") %>% paste0(".", tolower(LIB), gsub("[.]","",VER), "-ACE"), # Add ACE filename
    Map = paste0(Z,"-",SYMA, M) %>% paste0(".jeff33.mapping_output.html") # Add mapping html file
    ) %>%
  dplyr::mutate(
    # ENDF6 = paste0("<a href='endf6/", ENDF6, "' target='_blank'>", icon1, "</a>"),
    # ACE = paste0("<a href='ace/", ACE, "' target='_blank'>", icon1, "</a>"),
    Map = paste0("<a href='maps/", Map, "' target='_blank'>", icon2, "</a>")
    ) %>%
  data.table::setnames(
    old=c('Z','M','SYMA'),   
    new=c('Atomic number','Isomeric state','Isotope') 
    ) %>%
  DT::datatable(
    filter='top', 
    #extensions = 'Buttons', 
    rownames=FALSE,
    escape=FALSE,
    options = list(
      pageLength=10,
      lengthMenu=list(c(10, 50, 100, 200, 500, -1), list('10', '50', '100', '200', '500', 'All')),
      autowidth=TRUE,
      order = list(0, 'asc'),
      columnDefs=list(
        list(width='10%', targets = 0),
        list(className='dt-center', targets = 0:4)
        )
      )
    )


```
  


<!-- Row -->
<!-- ------ -->



<!-- ### **Access Files Individually** -->

<!-- ```{r ndec_table} -->
<!-- htmltools::includeHTML("ndec_jeff33.html") -->
<!-- ``` -->


```{r}
selected_MF <-31
```


```{r child='MF_COVA_section.Rmd'}
```


```{r}
selected_MF <-32
```


```{r child='MF_COVA_section.Rmd'}
```


```{r}
selected_MF <-33
```


```{r child='MF_COVA_section.Rmd'}
```


```{r}
selected_MF <-34
```


```{r child='MF_COVA_section.Rmd'}
```


```{r}
selected_MF <-35
```


```{r child='MF_COVA_section.Rmd'}
```


```{r}
selected_MF <-40
```


```{r child='MF_COVA_section.Rmd'}
```


