---
title: "Nuclear Data Mapping"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme : sandstone #readable #spacelab
    logo: www/logo.jpg
    includes:
      after_body: html/footer.html
    #css: mystyles.css
params:
  X : "H"
  A : 1
  M : "g"
  LIB : "JEFF"
  VER : "3.3"
  LIB2 : "JEFF"
  VER2 : "3.2"
  SDIR : "./"
  
---
<style>                     
.navbar {
  background-color:white;
  border-color:gray;
}
.navbar-brand {
color:DarkSlateGray!important;
}
.dataTables_wrapper{
font-family: helvetica;
font-size: 11px; 
}

</style>  

```{r setup, include=FALSE, cache = F}
library(plotly)
library(shinythemes)
library(shinyjs)
library(DT)
library(data.table)
library(dplyr)
library(flexdashboard)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
# source(paste0(params$SDIR, '/global.R'))
load(paste0(params$SDIR, 'df.RData'))

#define parameters other than params 
mLIBVER <- paste(params$LIB, params$VER, sep = "-")
mLIBVER2 <- paste(params$LIB2, params$VER2, sep = "-")
mSYMAM <- paste(params$X, params$A, params$M, sep = "-")

#for use by datatables :
pdf <- df %>% subset(X==params$X & A==params$A & M==params$M & LIB==params$LIB & VER==params$VER)
tot <- dim(pdf)[1]

# preparing datatables
pdfo <- df %>% subset(X==params$X & A==params$A & M==params$M)
lib2 <- pdfo %>% subset(LIB==params$LIB2 & VER==params$VER2,
                        select = c('MFDES', 'MTDES', 'MF', 'MT', 'LIBVERORIG'))
lib1 <- pdfo %>% subset(LIB==params$LIB & VER==params$VER,
                        select = c('MFDES', 'MTDES', 'MF', 'MT', 'LIBVERORIG'))
comp <- merge(lib1, lib2, by = c('MFDES', 'MTDES', 'MF', 'MT'), all=TRUE) %>%
  data.table::setnames(
    old=c("LIBVERORIG.x","LIBVERORIG.y"),
    new=c("LIB1","LIB2")
    ) %>%
  data.table::setnames(
    old=c("MFDES","MTDES"),
    new=c("MF TYPE","MT TYPE")
    ) %>%
  arrange(MF, MT) # sort dataframe by MF (first) and MT

#counting : 
totalupdated <- dim( comp %>% subset(LIB1!=LIB2 & !is.na(LIB1) & !is.na(LIB2)) )[1]
totunchanged <- dim( comp %>% subset(LIB1==LIB2) )[1]
newinlib1 <- dim( comp %>% subset(is.na(LIB2)) )[1]
erasedfromlib2 <- dim( comp %>% subset(is.na(LIB1)) )[1]

comp[is.na(comp)] <- 'NA'

if( totalupdated > 0 ) UpdatedColor <- "#b3ffb3" else UpdatedColor <-"Gray"
if( newinlib1 > 0 ) NewColor <- "#b3ffb3" else NewColor <-"Gray"
if( erasedfromlib2 > 0 ) ErasedColor <- "#ffb3b3" else ErasedColor <-"Gray"

LIBLINK <-"https://www.oecd-nea.org/dbdata"
```

Map
================

```{r child=paste0(params$SDIR, 'barheader_lib.Rmd')}
```

### MF/MT map {data-height=500}

```{r plotmap}
title <- paste(mSYMAM," from ", mLIBVER)

axisfont <- list(
  family = "Helvetica",
  size = 14,
  color = "blue"
)
    
yaxis=list(titlefont= axisfont)
xaxis=list(
  titlefont= axisfont,
  title = "MT",
  zeroline = FALSE,
  showline = FALSE,
  showticklabels = TRUE,
  showgrid = TRUE,
  tickangle=80
)
    
#changing column names for better readability in tooltip : 
pdf %>% setnames(old=c("MFDES","MTDES", "LIBVERORIG"), new=c("Type","Reaction", "Matches"))
g <- ggplot(pdf, aes(x=MT, y=MF, Type=Type, Reaction=Reaction, fill = Matches)) + 
  geom_tile(color="white") +
  scale_y_discrete(drop = FALSE) +
  scale_fill_manual(values = my_colors) +
  # theme_light() +
  theme_minimal() +
  # theme_classic() + 
  theme(
    legend.title = element_blank(),
    panel.grid.major = element_line(linetype = "dashed"),
    axis.line = element_line(size = 0.5, colour = "grey50"),
    plot.background = element_rect(fill="white"), #can be 'darkseagreen' too...
    plot.margin = unit(c(0.7, 0, 2, 1), "cm") #top, right, bottom, left
    )
p <- ggplotly(g, width = 1200, height = 500) %>%
  config(
    displayModeBar = 'pan',
    showLink=FALSE,
    senddata=FALSE,
    editable=FALSE,
    displaylogo=FALSE,
    collaborate=FALSE,
    cloud=FALSE,
    modeBarButtonsToRemove=c('select2d', 'lasso2d','hoverClosestCartesian', 'hoverCompareCartesian')
    ) %>%
  layout(#title=title,
    autosize = F,
    yaxis=yaxis ,
    xaxis=xaxis ,
    showlegend = TRUE
    )
p
#plotly_IMAGE(p, format = "png", out_file = "plotmap.png")
```
   
Updated
===========

```{r child=paste0(params$SDIR, 'barheader_table.Rmd')}
```

### **Updated** sections in `r mLIBVER` file,  with respect to reference : `r mLIBVER2`  
```{r table_updated} 
comp %>% subset(LIB1!=LIB2 & LIB1!="NA" & LIB2!="NA") %>% # diff occurrences
  data.table::setnames(old=c("LIB1", "LIB2"),
                       new=c(paste0(mLIBVER,' matching'), paste0(mLIBVER2,' matching'))) %>%
  datatable(filter = 'top',
            rownames = F,
            options = list(
              pageLength=10,
              lengthMenu=list(c(10, 50, 100, 200, 500, -1), list('10', '50', '100', '200', '500', 'All')),
              rownames=FALSE,
              autowidth=FALSE,
              #scrollY="1000vh",
              columnDefs=list(list(className='dt-center', targets=1:5))
              )
            )
```


New
===========

```{r child=paste0(params$SDIR, 'barheader_table.Rmd')}
```

### **New** sections in `r mLIBVER` file,  with respect to reference : `r mLIBVER2` 
```{r table_new} 
comp %>% subset(LIB2=="NA") %>% # new in LIB1
  data.table::setnames(old=c("LIB1","LIB2"), new=c(paste0(mLIBVER,' matching'), paste0(mLIBVER2,' matching'))) %>%
  datatable(filter = 'top',
            rownames = F,
            options = list(
              pageLength=10,
              lengthMenu=list(c(10, 50, 100, 200, 500, -1), list('10', '50', '100', '200', '500', 'All')),
              rownames=FALSE,
              autowidth=FALSE,
              #scrollY="1000vh",
              columnDefs=list(list(className='dt-center', targets=1:5))
              )
            )
```






Unchanged
===========

```{r child=paste0(params$SDIR, 'barheader_table.Rmd')}
```

### **Unchanged** sections in `r mLIBVER` file, with respect to reference : `r mLIBVER2` 
```{r table_same} 
comp %>% subset(LIB1==LIB2) %>% # same occurrences
  data.table::setnames(old=c("LIB1","LIB2"),
                       new=c(paste0(mLIBVER,' matching'), paste0(mLIBVER2,' matching'))) %>%
  datatable(filter = 'top',
            rownames = F,
            options = list(
              pageLength=10,
              lengthMenu=list(c(10, 50, 100, 200, 500, -1), list('10', '50', '100', '200', '500', 'All')),
              rownames=FALSE,
              autowidth=FALSE,
              #scrollY="1000vh",
              columnDefs=list(list(className='dt-center', targets=1:5))
              )
            )
```


Erased
===========

```{r child=paste0(params$SDIR, 'barheader_table.Rmd')}
```

### **Erased** sections in `r mLIBVER` file that were present in reference : `r mLIBVER2`
```{r table_erased} 
comp %>% subset(LIB1=="NA") %>%
data.table::setnames(old=c("LIB1","LIB2"),
                     new=c(paste0(mLIBVER,' matching'), paste0(mLIBVER2,' matching'))) %>%
datatable(filter = 'top',
          rownames = F,
          options = list(
            pageLength=10,
            lengthMenu=list(c(10, 50, 100, 200, 500, -1), list('10', '50', '100', '200', '500', 'All')),
            rownames=FALSE,
            autowidth=FALSE,
            #scrollY="1000vh",
            columnDefs=list(list(className='dt-center', targets=1:5))
            )
          )
```

